Editing Process Reflection

### 2024-12-06 paper/editing.Rmd
Reduced font size and changed documentclass to article.

---
title: "Editing Process Reflection"
author: 
  - name: "Raghav Sinha"
  - name: "Ziqi Zhu"
  - name: "Chris McWatt"
date: "`r Sys.Date()`"
date-format: long
abstract: ""
number-sections: false
format:
  pdf:
    toc: false
    number-sections: false
    colorlinks: true
editor: 
  markdown: 
    wrap: 72
---

>>>>

---
title: "Editing Process Reflection"
author: 
  - name: "Raghav Sinha"
  - name: "Ziqi Zhu"
  - name: "Chris McWatt"
date: "`r Sys.Date()`"
date-format: long
abstract: ""
number-sections: false
format:
  pdf:
    documentclass: article
    toc: false
    number-sections: false
    colorlinks: true
    margin-top: 0.75in
    margin-bottom: 0.75in
    margin-left: 0.75in
    margin-right: 0.75in
editor: 
  markdown: 
    wrap: 72
---
